\documentclass[12pt]{article}
\usepackage{pmmeta}
\pmcanonicalname{AnyTopologicalSpaceWithTheFixedPointPropertyIsConnected}
\pmcreated{2013-03-22 13:56:35}
\pmmodified{2013-03-22 13:56:35}
\pmowner{yark}{2760}
\pmmodifier{yark}{2760}
\pmtitle{any topological space with the fixed point property is connected}
\pmrecord{12}{34705}
\pmprivacy{1}
\pmauthor{yark}{2760}
\pmtype{Theorem}
\pmcomment{trigger rebuild}
\pmclassification{msc}{47H10}
\pmclassification{msc}{54H25}
\pmclassification{msc}{55M20}

\endmetadata

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}

% used for TeXing text within eps files

\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}

% The below lines should work as the command
% \renewcommand{\bibname}{References}
% without creating havoc when rendering an entry in 
% the page-image mode.
\makeatletter
\@ifundefined{bibname}{}{\renewcommand{\bibname}{References}}
\makeatother

\newcommand*{\norm}[1]{\lVert #1 \rVert}
\newcommand*{\abs}[1]{| #1 |}
\renewcommand{\emptyset}{\varnothing}
\begin{document}
\PMlinkescapeword{property}

{\bf Theorem}
Any topological space with the \PMlinkname{fixed-point property}{FixedPointProperty} is connected.

{\bf Proof.}
We will prove the contrapositive.
Suppose $X$ is a topological space which is not connected.
So there are non-empty disjoint open sets $A,B\subseteq X$ such
that $X=A\cup B$. Then there are elements $a\in A$ and $b\in B$, and
we can define a function $f\colon X\to X$ by
$$ f(x) = \left\{ \begin {array}{ll} a, & \mbox{when} \, x\in B, \\
 b, & \mbox{when} \, x\in A. \\
 \end{array} \right. $$
Since $A\cap B=\emptyset$ and $A\cup B=X$, the function $f$ is well-defined.
Also, $a\notin B$ and $b\notin A$, so $f$ has no fixed point.
Furthermore, if $V$ is an open set in $X$, a short calculation shows that
$f^{-1}(V)$ is $\emptyset, A,B$ or $X$, all of which are open sets.
So $f$ is continuous, and therefore $X$ does not have the fixed-point property.
$\Box$

\begin{thebibliography}{9}
 \bibitem{jameson} G.J. Jameson, \emph{Topology and Normed Spaces},
 Chapman and Hall, 1974.
\bibitem{ward} L.E. Ward, \emph{Topology, An Outline for a First Course},
Marcel Dekker, Inc., 1972.
 \end{thebibliography}
%%%%%
%%%%%
\end{document}
